First steps towards a formalization of Forcing

### 2018-11-16 LSFA/isabelle-zf.tex
Pocos cambios

% locales

>>>>

Let us close this section with a brief comment about the facilities
provided by the Isabelle framework. The edition is done in an IDE
called \texttt{jEdit}, which is bundled with the standard Isabelle
distribution; it offers the user a fair amount of tools in order to
manage theory files, searching for theorems and concepts spread
through the source files, and includes tracing utilities for the
automatic tools. A main feature is a window showing the \emph{proof
  state}, where the active (sub)goals are shown, along with the
already obtained results and possibly errors.

Isabelle proofs can be written in two dialects.  The older one, and
also more basic, follows a procedural approach, where one applies
several tactics in order to decompose the goal into simpler ones and
then solving them (with the aid of automation); the original work by
Paulson used this method. Under this approach proofs are constructed
bottom-up resulting in proof-scripts that conceal the mathematical
reasoning behind the proof, since the intermediate steps are only
shown in the proof state. For this reason, the proof language
\emph{Isar} was developed, starting with Wenzel's
work~\cite{DBLP:conf/tphol/Wenzel99}. Isar is mostly declarative, and
its main purpose is to construct \emph{proof documents} that (in
principle) can be read and understood without the need of running the
code.

We started this development using the procedural approach, but soon
after we realized that for our purposes the Isar language was far more
appropriate.
